Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean (*Phaseolus vulgaris*) in the United States

### 2017-11-06 doc/manuscript/manuscript.Rmd
add note about MX population
This addresses #15. I still am not exactly sure how to
treat this issue. I think some time away from this document may
help with it.
add figure for MCG delination

@@

Nearly all population genetic studies of *S. sclerotiorum* employ a macroscopic assay to determine mycelial compatibility, the ability for fungal hyphae from different colonies to appear to grow together without forming a barrier of dead cells between them (known as a barrage line) [@leslie1993fungal; @sirjusingh2001characterisation].
Mycelial compatibility has been used as a proxy for vegetative compatibility, a fungal trait controlled by several independent genes controlling the ability for two hyphae to fuse and grow as a single unit [@leslie1993fungal; @schafer2006optimized].
Because of the genetic connection to vegetative compatibility, two isolates that are mycelially compatible were considered clones [@leslie1993fungal]; but correlation with genetic markers, such as microsatellites, have shown mixed results [@ford1995heterokaryon; @micali2003independence; @jo2008reassessment; @attanayake2012genetic; @papaioannou2014barrage; @lehner2017independently].
However, a question remains about the relationship between mycelial compatibility groups and clonal genotypes.

@@

The widespread nature of multilocus haplotypes in both wmn and production fields with relatively small values of $P_{sex}$ may indicate the spread of inoculum between regions. 
While seedborne transmission is thought to be of insignificant epidemiological importance [@strausbaugh2003management], it has since been shown that *S. sclerotiorum* infections can be transmitted through seed [@botelho2013performance].
Thus, we hypothesize that shared haplotypes between populations may arise due to transmission events of seed or sclerotia.
This could explain the fact that we see shared genotypes with low $P_{sex}$ values shared between Australia, France, and the United States.
While we speculate that these transmission events are rare due to the genetic structuring by Region, these results suggest that seedborne infections may indeed reflect a source of inoculum.
This may, in turn increase the risk of introducing new sources of genetic variation through potential outcrossing events.

@@

>>>>

<!-- Include discussion on symptoms and economic damage leading in to cultivar discussion? -->

@@

Nearly all population genetic studies of *S. sclerotiorum* employ a macroscopic assay to determine mycelial compatibility, the ability for fungal hyphae from different colonies to appear to grow together without forming a barrier of dead cells between them (known as a barrage line, Fig. \@ref(mcg-fig)B) [@leslie1993fungal; @sirjusingh2001characterisation].
Mycelial compatibility has been used as a proxy for vegetative compatibility, a fungal trait controlled by several independent genes controlling the ability for two hyphae to fuse and grow as a single unit (Fig. \@ref(mcg-fig)A) [@leslie1993fungal; @schafer2006optimized].
Because of the genetic connection to vegetative compatibility, two isolates that are mycelially compatible were considered clones [@leslie1993fungal]; but correlation with genetic markers, such as microsatellites, have shown mixed results [@ford1995heterokaryon; @micali2003independence; @jo2008reassessment; @attanayake2012genetic; @papaioannou2014barrage; @lehner2017independently].
However, a question remains about the relationship between mycelial compatibility groups and clonal genotypes.

@@

The widespread nature of multilocus haplotypes in both wmn and production fields with relatively small values of $P_{sex}$ may indicate the spread of inoculum between regions. 
While seedborne transmission is thought to be of insignificant epidemiological importance [@strausbaugh2003management], it has since been shown that *S. sclerotiorum* infections can be transmitted through seed [@botelho2013performance].
Thus, we hypothesize that shared haplotypes between populations may arise due to transmission events of seed or sclerotia.
This could explain the fact that we see shared genotypes with low $P_{sex}$ values shared between Australia, France, and the United States.
While we speculate that these transmission events are rare due to the genetic structuring by Region, these results suggest that seedborne infections may indeed reflect a source of inoculum.
This may, in turn increase the risk of introducing new sources of genetic variation through potential outcrossing events.
<!-- I was also interested in more interpretation/analysis as to why the Mexican population did not have MLH shared with any other regions, the absence of clarity on this is done at a loss. -->

@@

![
Example of MCG test plates showing (A) a compatible reaction with mycelia from two strains overgrowing each other and (B) an incompatible reaction with a barrage line of dead tissue forming between the two strains. Photo Credit: Rebecca Higgens.
](images/mcg-trimmed.png){#mcg-fig width=100%}
